---
title: "Worksheet 2"
author: "Elijah June G. Tuares"
date: "2024-09-25"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

a. Sequence from -5 to 5. Write the R code and its output.
Describe its output.
```{r}
seq(-5, 5)

```
It is a numeric vector containing 11 elements from -5 to 5.

b. x <- 1:7. What will be the value of x?
```{r}
x <- 1:7
x
```
The value of x ranges from 1 to 7



2.Create a vector using seq() function
a. seq(1, 3, by=0.2) # specify step size
Write the R script and its output. Describe the output.
```{r}
vector <- seq(1, 3, by=0.2)
print(vector)
```
It is a numeric vector containing a sequence of numbers that starts at 1 and ends at 3, with each successive number incrementing by 0.2.



3. A factory has a census of its workers. There are 50 workers in total. The following
list shows their ages: 34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35,
24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18.

a. Access 3rd element, what is the value?
```{r}
ages <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
          22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37,
          43, 53, 41, 51, 35, 24, 33, 41, 53, 40, 18, 44, 38,
          41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)

ages[3]
```
The value is 22.

b. Access 2nd and 4th element, what are the values?
```{r}
ages <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
          22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37,
          43, 53, 41, 51, 35, 24, 33, 41, 53, 40, 18, 44, 38,
          41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)

ages[c(2, 4)]
```
The Values are 28 and 36 respectively.

c. Access all but the 4th and 12th element is not
included. Write the R script and its output.
```{r}
ages <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
          22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37,
          43, 53, 41, 51, 35, 24, 33, 41, 53, 40, 18, 44, 38,
          41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)

ages[-c(4, 12)]
```
The output is a vector containing all the ages except for the 4th element (36) and the 12th element (31).



4. Create a vector x <- c("first"=3, "second"=0, "third"=9). Then named the
vector, names(x).
a. Print the results. Then access x[c("first", "third")].
Describe the output.
```{r}
x <- c("first" = 3, "second" = 0, "third" = 9)
print(names(x))
```


b. Write the code and its output.
```{r}
x[c("first", "third")]

```
The first output line shows the names of the vector.
The second output line displays the values of the vector elements accessed by their names.

5. Create a sequence x from -3:2.
a. Modify 2nd element and change it to 0;
x[2] <- 0
x
Describe the output.
```{r}
x <- -3:2
```

b. Write the code and its output.
```{r}
x[2] <- 0
```
The output shows the modified vector x which are -3, 0, -1, 0, 1, 2.

6. The following data shows the diesel fuel purchased by Mr. Cruz.
a. Create a data frame for month, price per liter (php)
and purchase-quantity (liter). Write the R scripts and
its output.
```{r}
month <- c("Jan", "Feb", "Mar", "Apr", "May", "June")
price_per_liter <- c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00)
purchase_quantity <- c(25, 30, 40, 50, 10, 45)

fuel_purchases <- data.frame(
  Month = month,
  Price_per_liter = price_per_liter,
  Purchase_quantity = purchase_quantity
)
print(fuel_purchases)
```

b. What is the average fuel expenditure of Mr. Cruz from
Jan to June? Note: Use ‘weighted.mean(liter,
purchase)‘. Write the R scripts and its output.
```{r}
fuel_data <- data.frame(
  Month = c("Jan", "Feb", "Mar", "Apr", "May", "June"),
  Price_per_liter <- c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00),
  Purchase_quantity <- c(25, 30, 40, 50, 10, 45)
)
print(fuel_data)

average_expenditure <- weighted.mean(fuel_data$Price_per_liter, fuel_data$Purchase_quantity)
cat("The average fuel expenditure from January to June is:", average_expenditure, "Php\n")
```


7. R has actually lots of built-in datasets. For example, the rivers data “gives the lengths
(in miles) of 141 “major” rivers in North America, as compiled by the US Geological
Survey”.
a. Type “rivers” in your R console.
Create a vector data with 7
elements, containing the number of elements (length)
in rivers, their sum (sum), mean (mean),
median(median), variance(var), standard deviation(sd),
minimum (min) and maximum (max).
data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers),
sd(rivers), min(rivers), max(rivers))
```{r}
data <- c(
  length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers), sd(rivers), min(rivers), max(rivers)    
)
```

b. What are the results?
It shows the answers to each elements.

c. Write the R scripts and its outputs.
```{r}
data
```


8.
a. Create vectors according to the above table.
Write the R scripts and its output.
```{r}

celebrity_names <- c("Tom Cruise", "Rolling Stones", "Oprah Winfrey", "U2", "Tiger Woods", "Steven Spielberg", "Howard Stern", "50 Cent", "Cast of the Sopranos", "Dan Brown", "Bruce Springsteen", "Donald Trump", "Muhammad Ali", "Paul McCartney", "George Lucas", "Elton John", "David Letterman", "Phil Mickelson", "J.K. Rowling", "Bradd Pitt", "Peter Jackson", "Dr. Phil McGraw", "Jay Leno", "Celine Dion", "Kobe Bryant")

power_ranking <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25)
pay <- c(67, 90, 225, 110, 90, 332, 302, 41, 52, 88, 55, 44, 55, 40, 233, 34, 40, 47, 75, 39, 45, 32, 35, 32, 31)

celebrity_names
power_ranking
pay
```

b. Modify the power ranking and pay of J.K. Rowling.
Change power ranking to 15 and pay to 90. Write the
R scripts and its output.
```{r}
celebrity_names[which(celebrity_names == "J.K. Rowling")] <- "J.K. Rowling"
power_ranking[which(celebrity_names == "J.K. Rowling")] <- 15
pay[which(celebrity_names == "J.K. Rowling")] <- 90

celebrity_names
power_ranking
pay
```

c. Create an excel file from the table above and save it
as csv file(PowerRanking). Import the csv file into
the RStudio. What is the R script?
```{r}

```

d. Access the rows 10 to 20 and save it as Ranks.RData.
Write the R script and its output.
```{r}

```


9. Download the Hotels-Vienna https://tinyurl.com/Hotels-Vienna
a. Import the excel file into your RStudio.
What is the R script?










