---
title: "RWorksheet_Tuares#1"
author: "Elijah June G. Tuares"
date: "2024-09-04"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Set up a vector named age, consisting of 34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,
51, 35, 24, 33, 41.
a. How many data points?
  there are 34 data points.
  
  
b. Write the R code and its output.
```{r}
  age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
  35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,
  51, 35, 24, 33, 41)
length(age)
```

2. Find the reciprocal of the values for age.
Write the R code and its output.
```{r}
  age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
  35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,
  51, 35, 24, 33, 41)
reciprocal_age <- 1 / age 
reciprocal_age
```

3. Assign also new_age <- c(age, 0, age).

```{r}
  age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
  35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,
  51, 35, 24, 33, 41)

newage <- c(age, 0, age)

print(newage)
```

What happen to the new_age?
  
  The c() function is utilized to concatenate the vectors, resulting in the new_age vector, which     comprises 69 elements: the initial 34 elements from the age vector, followed by a single 0,    and finally, the duplicate 34 elements from the age vector.
  
4. Sort the values for age.
Write the R code and its output.
```{r}
sort(age)
```

5. Find the minimum and maximum value for age.
Write the R code and its output.
```{r}
  min_age <- min(age)
  max_age <- max(age)
  print(paste("Minimum age", min_age))
  print(paste("Maximum age", max_age))
```

6. Set up a vector named data, consisting of 2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5,
2.3, 2.5, 2.3, 2.4, and 2.7.
a. How many data points?

There are 12 data points.

b. Write the R code and its output.

```{r}
  data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5, 2.3, 2.4, 2.7)
  num_data_points <- length(data)
  print(paste("Data points:", num_data_points))
  print(data)
```

7. Generates a new vector for data where you double every value of the data. | What
happen to the data?

The data doubles in amount.

8. Generate a sequence for the following scenario:

8.1 Integers from 1 to 100.

```{r}
  seq1 <- 1:100
  print(paste("Sequence of integers from 1 to 100:"))
  print(seq1)
```


8.2 Numbers from 20 to 60

```{r}
  seq2 <- 20:60
  print(paste("Sequence of numbers from 20 to 60:"))
  print(seq2)
```

*8.3 Mean of numbers from 20 to 60

```{r}
  mean_seq2 <- mean(seq2)
  print(paste("Mean of 20 to 60:", mean_seq2))
```

*8.4 Sum of numbers from 51 to 91

```{r}
  sum_seq3 <- sum(51:91)
  print(paste("Sum of 51 to 91:", sum_seq3))
```

*8.5 Integers from 1 to 1,000

```{r}
  seq4 <- 1:1000
  print(paste("Sequence of integers from 1 to 1,000:"))
  print(seq4)
```

  a. How many data points from 8.1 to 8.4?_______
  
  There are 182 data points from 8.1 to 8.4
  
  b. Write the R code and its output from 8.1 to 8.4.
  
```{r}
  seq1 <- 1:100
  print(seq1)
  seq2 <- 20:60
  print(seq2)
  mean_seq2 <- mean(20:60)
  print(mean_seq2)
  sum_seq3 <- sum(51:91)
  print(sum_seq3)
```
  
  c. For 8.5 find only maximum data points until 10.
  
```{r}
  seq5 <- 1:1000
  print(seq5[1:10])
```
  
  9. *Print a vector with the integers between 1 and 100 that are not divisible by 3, 5 and
7 using filter option.
Filter(function(i) { all(i %% c(3,5,7) != 0) }, seq(100))
Write the R code and its output.

```{r}
  result <- Filter(function(i) { all(i %% c(3,5,7) != 0) }, 1:100)

  print(result)
```

11. List all the natural numbers below 25 that are multiples of 3 or 5.
Find the sum of these multiples.

a. How many data points from 10 to 11?

 3 + 5 + 6 + 9 + 10 + 12 + 15 + 18 + 20 + 21 + 24 = 143.

b. Write the R code and its output from 10 and 11.

```{r}
multiples <- c(3, 5, 6, 9, 10, 12, 15, 18, 20, 21, 24)
sum_multiples <- sum(multiples)
print(paste("Sum of multiples:", sum_multiples))
seq1 <- 10:11
```

12. Statements can be grouped together using braces ‘{’ and ‘}’. A group of statements
is sometimes called a block. Single statements are evaluated when a new line is typed
at the end of the syntactically complete statement. Blocks are not evaluated until a
new line is entered after the closing brace.
Enter this statement:

x <- {0 + x + 5 + }

Describe the output.

13. *Set up a vector named score, consisting of 72, 86, 92, 63, 88, 89, 91, 92, 75,
75 and 77. To access individual elements of an atomic vector, one generally uses the
x[i] construction.

```{r}
score <- c(72, 86, 92, 63, 88, 89, 91, 92, 75, 75, 77)
```

Find x[2] and x[3]. Write the R code and its output.

```{r}
x2 <- score[2]
x3 <- score[3]
print(paste("x[2] =", x2))
print(paste("x[3] =", x3))
```

14. *Create a vector a = c(1,2,NA,4,NA,6,7).
a. Change the NA to 999 using the codes print(a,na.print="-999").

```{r}
a <- c(1, 2, NA, 4, NA, 6, 7)
print(a)
print(a, na.print="-999")
```

b. Write the R code and its output. Describe the output.

The first line of the output displays the original vector 'a' containing 'NA' values. The second line shows the modified vector 'a', where the 'NA' values have been replaced with '-999'. The 'na.print' argument in the 'print()' function is used to define the string that will replace 'NA' values when the vector is printed.

15. A special type of function calls can appear on the left hand side of the assignment
operator as in > class(x) <- "foo".
Follow the codes below:
name = readline(prompt="Input your name: ")
age = readline(prompt="Input your age: ")
print(paste("My name is",name, "and I am",age ,"years old."))
print(R.version.string)
What is the output of the above code?

```{r}
name = readline(prompt="Input your name: ")
age = readline(prompt="Input your age: ")
print(paste("My name is",name, "and I am",age ,"years old."))
print(R.version.string)
```

The output of the code depends on the user's provided input.