---
title: "Worksheet 3b"
author: "Elijah June G. Tuares"
date: "2024-10-17"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Create a data frame using the table below.
a. Write the codes.
```{r}
library(dplyr)
Respondents <- c(seq(1,20))
Sex <- c(2,2,1,2,2,2,2,2,2,2,1,2,2,2,2,2,2,2,1,2)
Father_Occupation <- c(1,3,3,3,1,2,3,1,1,1,3,2,1,3,3,1,3,1,2,1)
PersonsAtHome <- c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6)
SiblingsAtSchool <- c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2)
TypeOfHouses <- c (1,2,3,1,1,3,3,1,2,3,2,3,2,2,3,3,3,3,3,2)

data_display <- data.frame(Respondents, Sex,Father_Occupation,PersonsAtHome,SiblingsAtSchool,TypeOfHouses)
data_display
```


b. Describe the data. Get the structure or the summary of the data
The dataset consists of responses from 20 individuals, providing details about their gender, with 7 males and 13 females. It also includes information about their fathers' occupations (coded as 1, 2, or 3), household sizes (ranging from 3 to 11 people), school-going siblings (ranging from 1 to 6), and the type of houses they reside in (coded as 1, 2, or 3). Conducting further analysis on these variables can uncover valuable insights.
summary(data_display)

c. Is the mean number of siblings attending is 5? 
No.

d. Extract the 1st two rows and then all the columns using the subsetting functions.
Write the codes and its output.
```{r}
data1 <- subset (data_display)[1:2, 2:6, drop=FALSE]
data1
```


e. Extract 3rd and 5th row with 2nd and 4th column. Write the codes and its result.
```{r}
data2 <- data_display[c(3,5), c(2,4)]
data2
```


f. Select the variable types of houses then store the vector that results as types_houses.
Write the codes.
```{r}
types_houses <- data_display[c(6)]
types_houses
```

g. Select only all Males respondent that their father occupation was farmer. Write the
codes and its output.
```{r}
selected_data <- data_display %>% select(1:6)
data3 <- selected_data[data_display$Sex == 1,]
data3
```


h.
```{r}
female <- selected_data[data_display$SiblingsAtSchool >= 5,]
female
```


2. Write a R program to create an empty data frame. Using the following codes:
```{r}
df = data.frame(Ints=integer(),
                Doubles=double(),Characters=character(),
                Logicals=logical(),
                Factors=factor(),
                stringsAsFactors=FALSE)
print("Structure of the empty dataframe:")
print(str(df))
```


3. Create a .csv file of this. Save it as HouseholdData.csv
a. Import the csv file into the R environment. Write the codes.
```{r}
RespondentsNew<-c(1,2,3,4,5,6,7,8,9,10)
SexNew<-c("Male", "Female", "Female", "Male", "Male", "Female", "Female", "Male", "Female", "Male")
FathersOccupationNew<-c(1,2,3,3,1,2,2,3,1,3)
PeAtHomeNew<-c(5,7,3,8,6,4,4,2,11,6)
SibAtSchoolNew<-c(2,3,0,5,2,3,1,2,6,2)
TypesofHousesNew<-c("Wood","Congrete","Congrete","Wood", "Semi-Congrete","Semi-Congrete","Wood","Semi-Congrete", "Semi-Congrete", "Congrete")
HouseholdData<-data.frame(
  RespondentsNew,
  SexNew,
  FathersOccupationNew,
  PeAtHomeNew, 
  SibAtSchoolNew, 
  TypesofHousesNew
)
HouseholdData

library(readr)
csv_file <- "HouseholdData.csv"
write.csv(HouseholdData, file = csv_file)
HouseholdData <- read.csv("HouseholdData.csv")

```


b. Convert the Sex into factor using factor() function and change it into integer.[Legend:
Male = 1 and Female = 2]. Write the R codes and its output.
```{r}
data_display1 <- factor(HouseholdData$SexNew, levels = c("Male" = 1, "Female" = 2))
sex_mapping <- c("Male" = 1, "Female" = 2)
data_display1<-as.integer(sex_mapping[HouseholdData$SexNew])
unique(data_display1)
unique(HouseholdData$SexNew)
```


c. Convert the Type of Houses into factor and change it into integer. [Legend: Wood
= 1; Congrete = 2; Semi-Congrete = 3]. Write the R codes and its output.
```{r}
data_display2 <- factor(HouseholdData$TypesofHousesNew, levels = c("Wood" = 1, "Congrete" = 2,"Semi-Congrete" = 3))
sex_mapping2 <- c("Wood" = 1, "Congrete" = 2,"Semi-Congrete" = 3)
data_display2 <- as.integer(sex_mapping2[HouseholdData$TypesofHousesNew])
unique(data_display2)
unique(HouseholdData$TypesofHousesNew)

```


d. On father’s occupation, factor it as Farmer = 1; Driver = 2; and Others = 3. What
is the R code and its output?
```{r}
data_display3 <- factor(HouseholdData$FathersOccupationNew, labels=c("Farmer" = 1, "Driver" = 2,"Others" = 3))
sex_mapping3 <- c("Farmer" = 1, "Driver" = 2,"Others" = 3)
data_display3 <- as.integer(sex_mapping3[HouseholdData$FathersOccupationNew])
unique(data_display3)
unique(HouseholdData$FathersOccupationNew)
```


e. Select only all females respondent that has a father whose occupation is driver. Write
the codes and its output.
```{r}
selected_data3 <- HouseholdData %>% select(2,3,4)
data4 <- selected_data3[HouseholdData$FathersOccupationNew == 2, ]
data4
```


f. Select the respondents that have greater than or equal to 5 number of siblings attending
school. Write the codes and its output.
```{r}
selected_data3 <- HouseholdData %>% select(2,6)
data4 <- selected_data3[HouseholdData$SibAtSchoolNew >= 5,]
data4
colnames(HouseholdData) <- c("Respondents", "Sex", "Fathers Occupation", "Persons At Home", "Siblings At School", "Type Of Houses")

```


4. Graph Analysis: This bar chart, titled "Sentiment of Tweets per Day," offers a clear summary of the emotions expressed on Twitter throughout July 2020. The chart classifies tweets into three groups: negative, neutral, and positive.

Negative Sentiment:
On certain days, such as July 15 and July 21, 2020, there was a marked rise in negative tweets, reflecting disapproval or criticism. These peaks suggest increased discussion or heightened concerns.

Neutral Sentiment:
Neutral sentiment encompasses tweets with a balanced and factual tone. Neutral sentiments were dominant across July 2020, particularly on July 14, 15, 17, 18, and 21, indicating widespread non-partisan discussions on these dates.

Positive Sentiment:
Positive sentiment tweets are distinguished by their upbeat and hopeful nature. Notably, positive tweets persisted even on days with higher negative sentiment, such as July 14, 15, 17, 18, and 21, hinting at optimism or resilience amid critical discussions.

In conclusion, the bar chart titled "Sentiment of Tweets per Day" sheds light on the emotional dynamics of Twitter in July 2020. It categorizes tweets into negative, neutral, and positive sentiments, pinpointing days like July 15 and July 21, 2020, where negative sentiment spiked, signaling intense discussions. Neutral tweets remained the majority throughout the month, while positive sentiment showcased optimism even during spikes of negativity.