---
title: "Worksheet 4a"
author: "Elijah June G. Tuares"
date: "2024-10-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. The table below shows the data about shoe size and height. Create a data frame.

a. Describe the data.

```{r}
household <- data.frame(
  Shoe_size = c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0, 11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0),
  Height = c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.5, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0),
  Gender = c("F", "F", "F", "F", "M", "F", "F", "F", "M", "F", "M", "F", "M", "M", "M", "M", "F", "F", "M", "F", "F", "M", "M", "F", "M", "M", "M", "M")
)

print(household)
```

\pagebreak

b. Create a subset by males and females with their corresponding shoe size and height.
What its result? Show the R scripts.

```{r}
males <- household[household$Gender == "M",]
females <- household[household$Gender == "F",]

print(males)
print(females)
```

c. Find the mean of shoe size and height of the respondents. Write the R scripts and its
result.
```{r}
mean(household$Shoe_size)
mean(household$Height)
```

d. Is there a relationship between shoe size and height? Why?

Yes
```{r}
cor(household$Shoe_size, household$Height)
```

\pagebreak

2. Construct character vector months to a factor with factor() and assign the result to
factor_months_vector. Print out factor_months_vector and assert that R prints out
the factor levels below the actual values.

```{r}
months <- c("March", "April", "January", "November", "January", 
            "September", "October", "September", "November", 
            "August", "January", "November", "November", 
            "February", "May", "August", "July", 
            "December", "August", "August", "September", 
            "November", "February", "April")

factor_months_vector <- factor(months)

print(factor_months_vector)

levels(factor_months_vector)
```

3. Then check the summary() of the months_vector and factor_months_vector. | Interpret the results of both vectors. Are they both equally useful in this case?
```{r}
direction <- c("East", "West", "North", "West", "North")
frequency <- c(1, 4, 3, 2, 1)
factor_direction <- factor(direction, levels = c("East", "West", "North"))
print(factor_direction)
```

4
```{r}
factor_data <- c("East", "West", "North")
frequency_vector <- c(1, 4, 3)
new_order_data <- factor(factor_data,levels = c("East","West","North"))
print(new_order_data)
```

5
```{r}
#a
data <- read.table("import_march.csv", header = TRUE, sep = ",")
```
```{r}
#b
data
```

6
```{r}
exhaustive_search <- function() {
  # Get input from the user and check if it's a valid number
  number <- suppressWarnings(as.integer(readline(prompt = "Please select a number between 1 and 50: ")))
  if (is.na(number)) {
    print("Invalid input. Please enter a number.")
  } else if (number < 1 || number > 50) {
    print("The number selected is beyond the range of 1 to 50")
  } else if (number == 20) {
    print(TRUE)
  } else {
    print(number)
  }
}
exhaustive_search()
```

7
```{r}
min_bills <- function(price) {
  bills <- c(1000, 500, 200, 100, 50)
  count <- 0
  for (bill in bills) {
    
    while (price >= bill) {
      price <- price - bill  
      count <- count + 1   
    }
  }
  return(count)
}
snack_price <- 2700
cat("Minimum number of bills needed:", min_bills(snack_price), "\n")
```
8
```{r}
# a
grades <- data.frame(
  Name = c("Annie", "Thea", "Steve", "Hanna"),
  Grade1 = c(85, 65, 75, 95),
  Grade2 = c(65, 75, 55, 75),
  Grade3 = c(85, 90, 80, 100),
  Grade4 = c(100, 90, 85, 90)
)
print(grades)
```
```{r}
# b
for (i in 1:nrow(grades)) {
  avg <- sum(grades[i, 2:5]) / 4
  print(paste(grades$Name[i], "'s average grade this semester is", avg))
}
```
```{r}
# c
for (j in 2:5) {
  avg_test <- mean(grades[,j])
  if (avg_test < 80) {
    print(paste("The", j-1, "test was difficult with an average score of", avg_test))
  }
}
```
```{r}
# d
for (i in 1:nrow(grades)) {
  highest_score <- grades[i, 2]  
  for (j in 3:5) {  
    if (grades[i, j] > highest_score) {
      highest_score <- grades[i, j]
    }
  }
  if (highest_score > 90) {
    print(paste(grades$Name[i], "'s highest grade this semester is", highest_score))
  }
}
```